Introduction to Marginal Structural Models

### 2019-04-23 msm_introduction.Rmd
updated code to use rsample instead of broom for bootstrapped estimates

I will use the tidyverse and broom package for this presentation.

```{r setup, message=F, warning=F}
library(tidyverse)
library(broom)
```

@@

```{r msm with boot estimates, echo = F}
# percentile method with broom
# g formula
set.seed(321)
boot_msm <- simdata %>% bootstrap(1000) %>% 
  do(tidy(MSModelR::g.formula(data = ., y = "Y", a = "A", q.model = "A+W1+A:W2",
            model.family = "gaussian", estimate = "diff")))
# iptw
set.seed(123)
boot_iptw <- simdata %>% bootstrap(1000) %>% 
  do(tidy(MSModelR::iptw(data = ., y="Y",a="A",w="W1+W2",estimate="diff")))

@@

# fill matrix for g formula 
estimates[1,1] <- "G-Formula"
estimates[1,2] <- round(quantile(boot_msm$x, 0.5),2)
estimates[1,3] <- round(quantile(boot_msm$x, 0.025),2)
estimates[1,4] <- round(quantile(boot_msm$x, 0.975),2)

# fill matrix for iptw
estimates[2,1] <- "IPTW"
estimates[2,2] <- round(quantile(boot_iptw$x, 0.5),2)
estimates[2,3] <- round(quantile(boot_iptw$x, 0.025),2)
estimates[2,4] <- round(quantile(boot_iptw$x, 0.975),2)

>>>>

I will use the tidyverse and rsample package for this presentation. Note, as of 2019, I use to use broom package, but bootstrapping functions have been depreciated in favor of rsample.

```{r setup, message=F, warning=F}
library(tidyverse)
library(rsample)
```

@@

```{r msm with boot estimates, echo = F}
# percentile method with broom
# g formula
set.seed(321)

# define simple substitution
simple_sub <- function(split){
  MSModelR::g.formula(data = analysis(split), y = "Y", a = "A", 
                      q.model = "A+W1+A:W2", 
                      model.family = "gaussian", estimate = "diff")
  }
# bootstrap using rsample package
boot_msm <- simdata %>% 
  bootstraps(times = 1000) %>% 
  mutate(coef = map(splits, simple_sub)) %>% 
  unnest(coef)

# iptw
set.seed(123)

iptw <- function(split){
  MSModelR::iptw(data = analysis(split), 
                 y="Y",a="A",w="W1+W2",estimate="diff")
  }

boot_iptw <- simdata %>% 
  bootstraps(times = 1000) %>% 
  mutate(coef = map(splits, iptw)) %>% 
  unnest(coef)

@@

# fill matrix for g formula 
estimates[1,1] <- "G-Formula"
estimates[1,2] <- round(quantile(boot_msm$coef, 0.5),2)
estimates[1,3] <- round(quantile(boot_msm$coef, 0.025),2)
estimates[1,4] <- round(quantile(boot_msm$coef, 0.975),2)

# fill matrix for iptw
estimates[2,1] <- "IPTW"
estimates[2,2] <- round(quantile(boot_iptw$coef, 0.5),2)
estimates[2,3] <- round(quantile(boot_iptw$coef, 0.025),2)
estimates[2,4] <- round(quantile(boot_iptw$coef, 0.975),2)
